UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/methodology.tex
Minor edits.

\subsection{Adversarial Networks}
\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
competes against an adversary. From a classification perspective, the generator network produces instances which actively attempt 
to `fool' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
instances coming from the dataset and `false' instances produced by the generator network.
%, and thus improve its classification accuracy.
In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and fool the 
discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original
GAN formulation, our goal is to solve the minimax problem:

@@

\end{tabular}
\label{fig:cgan_samples}
\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
Bottom row: Generated samples.}
\end{figure}

>>>>

\subsection{Adversarial Networks}
\nostarnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
competes against an adversary. From a classification perspective, the generator network produces instances which actively attempt 
to `fool' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
instances coming from the dataset and `false' instances produced by the generator network.
%, and thus improve its classification accuracy.
In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and fool the 
discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original
GAN formulation, our goal is to solve the minimax problem:

@@

\end{tabular}
\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
Bottom row: Generated samples.}
\label{fig:cgan_samples}
\end{figure}
